Figures

### 2019-10-31 Analysis/Figures_in_R.Rmd
Fig script up

>>>>

## Iris example

```{r}
## Preparing the dataset
colnames(iris)[1:4] <- gsub("\\.", "\n", colnames(iris)[1:4])
rownames(iris) <- c(paste0("setosa", which(iris[,5] == "setosa")),
                    paste0("versicolor", which(iris[,5] == "versicolor")-50),
                    paste0("virginica", which(iris[,5] == "virginica")-100))

## Morphospaces:
## No transformations
write.csv(head(iris[, -5]), file = "../Writing/Figures/trait.space.no_trans.csv")

## Distance matrix
iris_dist <- dist(iris[, -5])
write.csv(round(head(as.matrix(iris_dist)[1:5, 1:5]), digits = 2), file = "../Writing/Figures/trait.space.distance.csv")

## Ordinations
iris_pca <- princomp(iris[, -5])$scores
write.csv(round(head(iris_pca), digits = 2), file = "../Writing/Figures/trait.space.pca.csv")
iris_pco <-cmdscale(iris_dist, k = 2)

## Visualisations
## biplots
col_var <- c("orange", "blue", "green")[as.factor(iris[,5])]
pdf(file = "../Writing/Figures/figure_methods_biplots.pdf", width = 5, height = 5)
plot(iris[, -5],
    pch = 19,
    col = col_var)
dev.off()

## PCO
pdf(file = "../Writing/Figures/figure_methods_PCO.pdf", width = 5, height = 5)

vars <- round(apply(iris_pco, 2, var)/sum(apply(iris_pco, 2, var))*100, 2)
plot(iris_pco,
    pch = 19,
    col = col_var,
    xlab = paste0("PCO 1 (", vars[1], "%)"),
    ylab = paste0("PCO 21 (", vars[2], "%)"),
    xlim = range(iris_pco),
    ylim = range(iris_pco))
dev.off()

## PCA
pdf(file = "../Writing/Figures/figure_methods_PCA.pdf", width = 5, height = 5)
vars <- round(apply(iris_pca, 2, var)/sum(apply(iris_pca, 2, var))*100, 2) 
ranges <- apply(iris_pca, 2, range)

par(mfrow = c(4,4), mar = c(1,1,1,1), oma = c(2,2,2,2))
## First row
# 1
plot(NULL, xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
text(0,0, paste0("PC 1\n(", vars[1], "%)"), cex = 1.9)
# 2
plot(iris_pca[, c(1,2)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(3)
# 3
plot(iris_pca[, c(1,3)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
# 4
plot(iris_pca[, c(1,4)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(3)
axis(4)

## Second row
# 1
plot(iris_pca[, c(2,1)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(2)
# 2
plot(NULL, xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
text(0,0, paste0("PC 2\n(", vars[2], "%)"), cex = 1.9)
# 3
plot(iris_pca[, c(2,3)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
# 4
plot(iris_pca[, c(2,4)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(4)

## Third row
# 1
plot(iris_pca[, c(3,1)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(2)
# 3
plot(iris_pca[, c(3,2)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
# 3
plot(NULL, xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
text(0,0, paste0("PC 3\n(", vars[3], "%)"), cex = 1.9)
# 4
plot(iris_pca[, c(3,4)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(4)

## Fourth row
# 1
plot(iris_pca[, c(4,1)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(1)
axis(2)
# 3
plot(iris_pca[, c(4,2)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
# 3
plot(iris_pca[, c(4,3)], xaxt = "n", yaxt = "n", ylab = "", xlab = "",
    pch = 19,
    col = col_var)
axis(1)
# 4
plot(NULL, xlim = c(-0.5, 0.5), ylim = c(-0.5, 0.5), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
text(0,0, paste0("PC 4\n(", vars[4], "%)"), cex = 1.9)
dev.off()
